An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-26 6_validation.tex
'beading strategy' ==> 'beading scheme'

\section{Validation}
In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
The data set is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 strategies discussed in \cref{sec_generalization}, namely 'Constant bead count' strategy with a bead count of $C=4$, the 'Centered' beading strategy, the 'Evenly distributed', and the 'Inward distributed' beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.

\subsection{Computational analysis}
Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed strategy. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.

@@

The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
We then add the original outline shape in reverse and perform a Vatti clipping operation \cite{Vatti2019clipping} which only keeps areas of positive winding number.
Because the reverse outline shape reduces the winding number of all extruded segments by one, only the overfill areas are left with a positive winding number.
In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing Vatti's clipping operation.
These triple extrusion areas count double toward the total amount of overfill.
The resulting overfill and underfill areas are visualized for the different toolpath strategies in the top of \cref{visualized_accuracy}.

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Uniform}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Center}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading strategies.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
}
\label{visualized_accuracy}
\end{figure*}

We calculated the total overfill and underfill areas of the different toolpath strategies applied on the data set. 
The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
The inward distributed strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the uniform strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.

@@

\caption{
Results of computational analysis of the results from applying the uniform width technique and various beading strategies using our framework to the data set.
Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
}
\end{figure*}

\subsubsection{Uniformity}
Depending on the printer hardware configuration, some bead widths might be difficult or impossible to produce.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
Also, large bead widths may cause the extruded material to bulge upwards instead of filling the required width.
Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
We visualize the bead widths resulting from the different strategies in the bottom of \cref{visualized_accuracy}.

To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
at intervals of \SI{1}{\micro\meter} along the toolpath.
From these sampled values, we calculated the mean bead width, and standard deviation per strategy.
\cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of \SI{10}{\micro\meter}.
We found that the mean width of our strategies 'Inward distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies 'Centered' and 'Constant bead count'. 
These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' strategies deviate less and infrequently from the nominal nozzle size compared to the other strategies.
We compared the width uniformity of the 6 outer beads for the strategies 'Inward distributed' and 'Evenly distributed', the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the 'Inward distributed' strategy clearly have more often the nominal width of \SI{400}{\micro\meter}, while the 'Evenly distributed' more often extrudes widths that deviate from the nominal width.

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive extrusion segments generated by each strategy.
The relative frequency of these angles is shown in \cref{smoothness}.
All strategies show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
The 'Inward distributed' strategy produces an order of magnitude less corners around \SI{30}{\degree}, compared to 'Evenly distributed'. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}.

@@

The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading strategy than the other strategies.

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
\caption{Wedge}\label{print_wedge}
\end{subfigure}
\caption{
A wedge shape printed using the uniform strategy, center deviation strategy and the inward distributed strategy.
The uniform and center deviation strategy show problems around certain model diameters.
}
\label{wedge_print}
\end{figure}

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
}
\caption{Uniform}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
}
\caption{Center deviation}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the uniform strategy, center deviation strategy and the inward distributed strategy.
The uniform technique produces distinct underfill areas.
The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed strategy produces the least defects.
}
\label{prints}
\end{figure}

>>>>

\section{Validation}
In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
The data set is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely 'Constant bead count' scheme with a bead count of $C=4$, the 'Centered' beading scheme, the 'Evenly distributed', and the 'Inward distributed' beading scheme, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.

\subsection{Computational analysis}
Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.

@@

The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
We then add the original outline shape in reverse and perform a Vatti clipping operation \cite{Vatti2019clipping} which only keeps areas of positive winding number.
Because the reverse outline shape reduces the winding number of all extruded segments by one, only the overfill areas are left with a positive winding number.
In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing Vatti's clipping operation.
These triple extrusion areas count double toward the total amount of overfill.
The resulting overfill and underfill areas are visualized for the different toolpath schemes in the top of \cref{visualized_accuracy}.

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Uniform}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Center}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading schemes.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
}
\label{visualized_accuracy}
\end{figure*}

We calculated the total overfill and underfill areas of the different toolpath schemes applied on the data set. 
The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
The inward distributed scheme has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the uniform scheme, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.

@@

\caption{
Results of computational analysis of the results from applying the uniform width technique and various beading schemes using our framework to the data set.
Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
}
\end{figure*}

\subsubsection{Uniformity}
Depending on the printer hardware configuration, some bead widths might be difficult or impossible to produce.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
Also, large bead widths may cause the extruded material to bulge upwards instead of filling the required width.
Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.

To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
at intervals of \SI{1}{\micro\meter} along the toolpath.
From these sampled values, we calculated the mean bead width, and standard deviation per scheme.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
We found that the mean width of our schemes 'Inward distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for schemes 'Centered' and 'Constant bead count'. 
These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' schemes deviate less and infrequently from the nominal nozzle size compared to the other schemes.
We compared the width uniformity of the 6 outer beads for the schemes 'Inward distributed' and 'Evenly distributed', the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the 'Inward distributed' scheme clearly have more often the nominal width of \SI{400}{\micro\meter}, while the 'Evenly distributed' more often extrudes widths that deviate from the nominal width.

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive extrusion segments generated by each scheme.
The relative frequency of these angles is shown in \cref{smoothness}.
All schemes show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
The 'Inward distributed' scheme produces an order of magnitude less corners around \SI{30}{\degree}, compared to 'Evenly distributed'. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}.

@@

The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
\caption{Wedge}\label{print_wedge}
\end{subfigure}
\caption{
A wedge shape printed using the uniform scheme, center deviation scheme and the inward distributed scheme.
The uniform and center deviation scheme show problems around certain model diameters.
}
\label{wedge_print}
\end{figure}

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
}
\caption{Uniform}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
}
\caption{Center deviation}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the uniform scheme, center deviation scheme and the inward distributed scheme.
The uniform technique produces distinct underfill areas.
The center deviation scheme shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed scheme produces the least defects.
}
\label{prints}
\end{figure}

### 2019-08-26 8_discussion.tex
'beading strategy' ==> 'beading scheme'

\subsection{Comparison of beading strategies}
The uniform beading scheme and the outer bead scheme are of little use to FDM printers, but they show the flexibility of our algorithmic framework.

@@

%The single bead strategy solves the underfill problem in regions where the model is more thin than the nozzle size.
%However, the strategy doesn't deal with the remaining area.
%In our visualization we print the outline of the remaining area which exposes an overextrusion problem.

The 'Constant bead count' strategy effectively deals with underfills, but generates orders of magnitude more overfills compared to the other strategies. 
Also, the strategy comes at the cost of greatly varying bead widths and an average bead width that is not close to the nominal bead width.
Note that most overfill areas occur near regions of alternating bead width.

@@

If we look at \cref{TEST_Center_accuracy} we can see that
the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width.
According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.

However, according to \cref{widthHistogram} the Centered strategy exhibits a lot wider range of bead widths than the Distributed strategies:
the standard deviation of the bead widths in the Centered strategy is approximately \SI{39}{\micro\meter}, while the standard deviation resulting from the Distributed strategies is approximately \SI{14}{\micro\meter}.
We can therefore state that the Distributed strategies result in bead widths closer to the nominal widths compared to the Centered strategy.
This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

The Inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.

However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the nominal bead width more often, which means that errors from inaccuracies due to deviation from the nominal bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all. 
Also, we find that compared to Evenly distributed, the Inward distributed strategy produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}). 
Therefore, when using the Inward distributed strategy the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.

@@

\subsection{Limitations}
In the beading strategies we discussed we set the length of the smoothed transitions to $t(n) = w_\text{pref}$.
That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
which might be difficult to accurately manufacture on some hardware.
While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around junctions in the toolpath, so this approach is inherently limited.
Our strategies require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms. \cite{tronvoll2019investigating}
Still inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.

@@

Taking a broader perspective, we note that our proposed inward distributed strategy is a pragmatic solution.
Rather than deriving some optimal beading strategy from a clear specification of the objective, we propose some arbitrary inward distributed beading strategy and show that it is better than the other beading strategies.
An optimal beading strategy can be derived if the objective is formalized terms of a unambiguous fitness function, but that would depend on the specific hardware setup and application for which toolpaths are generated.
This manuscript is therefore limited to showing the flexibility and versatility of the framework, rather than deriving an optimal beading strategy.

>>>>

\subsection{Comparison of beading schemess}
The uniform beading scheme and the outer bead scheme are of little use to FDM printers, but they show the flexibility of our algorithmic framework.

@@

%The single bead scheme solves the underfill problem in regions where the model is more thin than the nozzle size.
%However, the scheme doesn't deal with the remaining area.
%In our visualization we print the outline of the remaining area which exposes an overextrusion problem.

The 'Constant bead count' scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemess. 
Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the nominal bead width.
Note that most overfill areas occur near regions of alternating bead width.

@@

If we look at \cref{TEST_Center_accuracy} we can see that
the centered beading scheme effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width.
According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.

However, according to \cref{widthHistogram} the Centered scheme exhibits a lot wider range of bead widths than the Distributed schemess:
the standard deviation of the bead widths in the Centered scheme is approximately \SI{39}{\micro\meter}, while the standard deviation resulting from the Distributed schemess is approximately \SI{14}{\micro\meter}.
We can therefore state that the Distributed schemess result in bead widths closer to the nominal widths compared to the Centered scheme.
This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

The Inward distributed beading scheme was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.

However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the nominal bead width more often, which means that errors from inaccuracies due to deviation from the nominal bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all. 
Also, we find that compared to Evenly distributed, the Inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}). 
Therefore, when using the Inward distributed scheme the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.

@@

\subsection{Limitations}
In the beading schemess we discussed we set the length of the smoothed transitions to $t(n) = w_\text{pref}$.
That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
which might be difficult to accurately manufacture on some hardware.
While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around junctions in the toolpath, so this approach is inherently limited.
Our schemess require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms. \cite{tronvoll2019investigating}
Still inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.

@@

Taking a broader perspective, we note that our proposed inward distributed scheme is a pragmatic solution.
Rather than deriving some optimal beading scheme from a clear specification of the objective, we propose some arbitrary inward distributed beading scheme and show that it is better than the other beading schemess.
An optimal beading scheme can be derived if the objective is formalized terms of a unambiguous fitness function, but that would depend on the specific hardware setup and application for which toolpaths are generated.
This manuscript is therefore limited to showing the flexibility and versatility of the framework, rather than deriving an optimal beading scheme.
